Demographics: The Sound of Teaching Music 1

### 2020-07-29 script/RNotebook/questionnaire.Rmd
add plot
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
```

@@

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
```

@@

### Error Rate: Plot
```{r plot, echo = FALSE}
p_hist <- ggplot(subset(df_exc, df_exc$Final == "include"), aes(x = ErrorRate)) +
  geom_histogram(position = "identity", alpha = .5, binwidth = .01)
plot(p_hist)
```
